\emeszida

### 2024-03-29 sigbovik/paper.tex
more citations

\section{Introduction}
The history of math is long, but the history of programming is longer.
Cuneiform, arguably the first writing in the world, is known for its sheep receipts and beer ration lists as well as copper complaints \cite{oppenheim1954}.
This article adds neural network programming to that vaunted list of human achievements.
A set of newly discovered cuneiform tablets preserve the mechanism for performing simple neural network calculations.
These methods, it seems, were used to calculate the lengths of triangles; a well known exercise preserved on the tablet known as Plimpton 322\footnote{And important and real introduction into this interesting object is found in \citet{robson2002}.}.
It is remarkable that no historian of math or cuneiform scholar has ever consider this possibility.
This paper covers the background, a description of the cuneogramming language, and includes a facsimile copy of the most important tablet as an appendix.

@@

Other ancient corpora which have resisted decipherment, and which boast a similar numeric component, may represent additional examples of ancient programming traditions.

>>>>

\section{Introduction}
The history of math is long, but the history of programming is longer.
Cuneiform, arguably the first writing in the world, is known for its sheep receipts and beer ration lists as well as complaints about substandard copper \cite{oppenheim1954} and women complaining at each other \cite{Matuszak2020}.
This article adds neural network programming to that vaunted list of human achievements.
A set of newly discovered cuneiform tablets preserve the mechanism for performing simple neural network calculations.
These methods, it seems, were used to calculate the lengths of triangles; a well known exercise preserved on the tablet known as Plimpton 322\footnote{And important and real introduction into this interesting object is found in \citet{robson2002}.}.
It is remarkable that no historian of math or cuneiform scholar has ever consider this possibility.
This paper covers the background, a description of the cuneogramming language, and includes a facsimile copy of the most important tablet as an appendix.

@@

Other ancient corpora which have resisted decipherment, and which boast a similar numeric component, may represent additional examples of ancient programming traditions \cite{kelley2022}.
